---
title: "NARA_S_Output"
author: "Toon Van Daele"
date: "28 februari 2018"
output: html_document
params:
  modelname: "rlw"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dbplyr)
library(RSQLite)
library(pander)
modelname <- params$modelname #"allsp"
path <- paste0("../data/data-out/", modelname, "/")
```

Generating output for NARA_S of model: **`r modelname`**

```{r loaddata}
db <- dbConnect(SQLite(), dbname = paste0(path, "df_probs.sqlite"))
df_probs <- tbl(db, "df_probs")
speclist <- readRDS(paste0(path, "speclist.RDS"))
```

Selection of models with AUC >= 0.7

```{r selecteval}
df_meval <- readRDS(paste0(path, "df_meval.RDS"))

sp_sel <- df_meval %>%
  filter(Eval.metric == "ROC", mean >= 0.7) %>%
  pull(sp_n)
remove(df_meval)

df_probs <- filter(df_probs, sp_n %in% sp_sel)
```

Total number of species modelled with mean ROC > 0.7 =  `r length(sp_sel)`


Get utm xy coordinates

```{r getxy}
df_proj_in <- readRDS(paste0(path, "df_proj_in.RDS"))
utmIDxy <- df_proj_in %>%
  filter(scen == "Current") %>%
  dplyr::select(utmID, X, Y)
remove(df_proj_in)
```

Calculate prevalence

```{r calcprevalence}
df_data_in <- readRDS(file = paste0(path, "df_data_in.RDS"))
nbutm <- nrow(df_data_in)

df_prev <- df_data_in %>%
  dplyr::select(speclist) %>%
  gather(key = sp_n, value = presence) %>%
  group_by(sp_n) %>%
  summarize(prevalence = sum(presence, na.rm = TRUE) / nbutm) %>%
  arrange(desc(prevalence))

df_prev <- df_prev %>%
  mutate(ranksp = row_number() / nrow(df_prev)) %>%
  mutate(exp = (1000000^(1 - prevalence)) / 1000000)
remove(df_data_in)

ggplot(df_prev, aes(x = prevalence)) + geom_histogram()

df_prev %>%
  gather(key = type, value = weight, -sp_n, -prevalence ) %>%
  ggplot(aes(x = prevalence, y = weight)) + geom_jitter() +
  facet_wrap(~type)
```

Get redlist weights

```{r redlistweights}
df_redlist <- readRDS(paste0(path, "df_redlist.RDS"))

df_redlist <- filter(df_redlist, !is.na(RLweging))

df_prev <- left_join(x = df_prev,
                      y = df_redlist %>%
                         dplyr::select(Soortcode, RLweging),
                      by = c("sp_n" = "Soortcode"))
remove(df_redlist)
```

join 'prev' and 'redlist' to probs

```{r jointoprobs}
df_probs <- df_probs %>%
  left_join(df_prev,
            by = "sp_n",
            copy = TRUE)
```

Calculate sums per utmgrid and differences between scenarios

```{r calcsums}
df_sum <- df_probs %>%
  group_by(utmID, projname) %>%
  summarise(probsum = sum(probs, na.rm = TRUE) / 1000,
            binsum = sum(bins, na.rm = TRUE),
            probsumw = sum(probs * ranksp, na.rm = TRUE) / 1000,
            binsumw = sum(bins * ranksp, na.rm = TRUE),
            binsumrl = sum(bins * ifelse(RLweging > 0, 1, 0), na.rm = TRUE),
            binsumrlw = sum(bins * RLweging, na.rm = TRUE)) %>%
  collect()
saveRDS(df_sum, file = paste0(path, "df_sum.RDS"))
```

Results: 'sum of probabilities'

```{r}
df_probsum <- df_sum %>%
  select(utmID, projname, probsum) %>%
  spread(key = projname, value = probsum) %>%
  mutate_at(vars(contains("kr")),
                  .funs = funs(v = . - get(paste0(modelname, "_Current")))) %>%
  left_join(utmIDxy, by = "utmID")

(p <- ggplot(df_probsum, aes(x = X, y = Y, colour = rlw_Current)) +
  scale_colour_gradientn(colours = rainbow(3)) +
  geom_point() + coord_fixed())
ggsave(paste0(path, "probsum.png"), p)

saveRDS(df_probsum, file = paste0(path, "df_probsum.RDS"))
write.table(df_probsum, file = paste0(path, "df_probsum.txt"),
            quote = FALSE, sep = ";", dec = ",", row.names = FALSE)

summary(df_probsum[-c(1, 11, 12)])
```

Results: 'sum of binaries'

```{r}
df_binsum <- df_sum %>%
  select(utmID, projname, binsum) %>%
  spread(key = projname, value = binsum) %>%
  mutate_at(vars(contains("kr")),
                  .funs = funs(v = . - get(paste0(modelname, "_Current")))) %>%
  left_join(utmIDxy, by = "utmID")

(p <- ggplot(df_binsum, aes(x = X, y = Y, colour = rlw_Current)) +
  scale_colour_gradientn(colours = rainbow(3)) +
  geom_point() + coord_fixed())
ggsave(paste0(path, "binsum.png"), p)

saveRDS(df_binsum, file = paste0(path, "df_binsum.RDS"))
write.table(df_binsum, file = paste0(path, "df_binsum.txt"),
            quote = FALSE, sep = ";", dec = ",", row.names = FALSE)

summary(df_binsum[-c(1, 11, 12)])
```

Results: 'weighted (ranks) sum of probabilities'

```{r}
df_probsumw <- df_sum %>%
  select(utmID, projname, probsumw) %>%
  spread(key = projname, value = probsumw) %>%
  mutate_at(vars(contains("kr")),
                  .funs = funs(v = . - get(paste0(modelname, "_Current")))) %>%
  left_join(utmIDxy, by = "utmID")

(p <- ggplot(df_probsumw, aes(x = X, y = Y, colour = rlw_Current)) +
  scale_colour_gradientn(colours = rainbow(3)) +
  geom_point() + coord_fixed())
ggsave(paste0(path, "probsumw.png"), p)

saveRDS(df_probsumw, file = paste0(path, "df_probsumw.RDS"))
write.table(df_probsumw, file = paste0(path, "df_probsumw.txt"),
            quote = FALSE, sep = ";", dec = ",", row.names = FALSE)

summary(df_probsumw[-c(1, 11, 12)])
```


Results: 'weighted (ranks) sum of binaries'

```{r}
df_binsumw <- df_sum %>%
  select(utmID, projname, binsumw) %>%
  spread(key = projname, value = binsumw) %>%
  mutate_at(vars(contains("kr")),
                  .funs = funs(v = . - get(paste0(modelname, "_Current")))) %>%
  left_join(utmIDxy, by = "utmID")

(p <- ggplot(df_binsumw, aes(x = X, y = Y, colour = rlw_Current)) +
  scale_colour_gradientn(colours = rainbow(3)) +
  geom_point() + coord_fixed())
ggsave(paste0(path, "binsumw.png"), p)

saveRDS(df_binsumw, file = paste0(path, "df_binsumw.RDS"))
write.table(df_binsumw, file = paste0(path, "df_binsumw.txt"),
            quote = FALSE, sep = ";", dec = ",", row.names = FALSE)

summary(df_binsumw[-c(1, 11, 12)])
```


Results: 'redlist weight > 0 sum of binaries'

```{r}
df_binsumrl <- df_sum %>%
  select(utmID, projname, binsumrl) %>%
  spread(key = projname, value = binsumrl) %>%
  mutate_at(vars(contains("kr")),
                  .funs = funs(v = . - get(paste0(modelname, "_Current")))) %>%
  left_join(utmIDxy, by = "utmID")

(p <- ggplot(df_binsumrl, aes(x = X, y = Y, colour = rlw_Current)) +
  scale_colour_gradientn(colours = rainbow(3)) +
  geom_point() + coord_fixed())
ggsave(paste0(path, "binsumrl.png"), p)

saveRDS(df_binsumrl, file = paste0(path, "df_binsumrl.RDS"))
write.table(df_binsumrl, file = paste0(path, "df_binsumrl.txt"),
            quote = FALSE, sep = ";", dec = ",", row.names = FALSE)

summary(df_binsumrl[-c(1, 11, 12)])
```


Results: 'weighted (redlist status) sum of binaries'

```{r}
df_binsumrlw <- df_sum %>%
  select(utmID, projname, binsumrlw) %>%
  spread(key = projname, value = binsumrlw) %>%
  mutate_at(vars(contains("kr")),
                  .funs = funs(v = . - get(paste0(modelname, "_Current")))) %>%
  left_join(utmIDxy, by = "utmID")

(p <- ggplot(df_binsumrlw, aes(x = X, y = Y, colour = rlw_Current)) +
  scale_colour_gradientn(colours = rainbow(3)) +
  geom_point() + coord_fixed())
ggsave(paste0(path, "binsumrlw.png"), p)

saveRDS(df_binsumrlw, file = paste0(path, "df_binsumrlw.RDS"))
write.table(df_binsumrlw, file = paste0(path, "df_binsumrlw.txt"),
            quote = FALSE, sep = ";", dec = ",", row.names = FALSE)

summary(df_binsumrlw[-c(1, 11, 12)])
```

```{r rank_plot}
make_rank_plot <- function(df) {
  p <- df %>%
    as.tibble() %>%
    dplyr::sample_n(4000) %>%
    select(rlw_Current, rlw_kr1, rlw_kr2, rlw_kr3, rlw_kr4) %>%
    gather(key = "scen", value = "aantal") %>%
    group_by(scen) %>%
    arrange(scen, aantal) %>%
    mutate(percent = row_number() / sample_size * 100) %>%
    ggplot(aes(x = percent, y = aantal, colour = scen)) + geom_path()
}
```
Ranking sum of probabilities

```{r cumul_probsum}
p <- make_rank_plot(df_probsum)
plot(p)
ggsave(paste0(path, "probsum_rank.png"), p)
```

Ranking sum of binaries

```{r}
p <- make_rank_plot(df_binsum)
plot(p)
ggsave(paste0(path, "binsum_rank.png"), p)
```

